Parallel Adaptive Importance Sampling

### 2017-02-03 cover_letter.tex
Cover letter finished

In the response letter, the associate editor stated that: \emph{"You will see that both referees reports are quite short -- that is my doing. I was aware (through the SIAM grapevine) that you had previously submitted this paper to SISC and that lengthy reviews had been obtained. So, in the interest of not using too much of people's time, I asked for indicative reviews."} This clearly indicates that this submission was not treated as a new submission, and the referees were instructed not to give a full review. Moreover, their reviews have in our view been unfairly coloured by the previous reviews from the SISC submission which were provided to them. In particular, they criticise us due to \emph{"the computed example provides no information about whether or not the proposed method will work in the (sizable) applications mentioned in your introduction."} However, all mentions of such sizable applications have been completely removed from the introduction.
% The suggested references from referee 2 are also all regarding MCMC algorithms for high dimensional problems, when this method is more aimed at complex posteriors in lower dimensions. Referee 2 also suggest that ``The adaptation only aims at learning the scale of the proposal, whereas the shape can be as (or more) important''. We have no idea where this criticism comes from since the entire point of the paper is that the proposal distribution learns the shape of the posterior distribution from the ensemble of particles.

@@

We are keen to resubmit the manuscript to SIAM/ASA JUQ for a second time. In order to address the issues that have arisen, we have provided three copies of the paper. The first is the original submission to SISC. The second is the version of the paper that was submitted to SIAM UQ, with the changes made highlighted. The third version is our new submission, with the newest changes highlighted. We also provide detailed descriptions of how the changes address the concerns of the referees.

@@

We thank you very much for your time and patience in dealing with this manuscript, and would like to apologise in our oversight in failing to provide these details at the time of the first submission to SIAM/ASA JUQ. We look forward to hearing from you in due course.

>>>>

In the response letter, the associate editor stated that: \emph{"You will see that both referees reports are quite short -- that is my doing. I was aware (through the SIAM grapevine) that you had previously submitted this paper to SISC and that lengthy reviews had been obtained. So, in the interest of not using too much of people's time, I asked for indicative reviews."} This clearly indicates that this submission was not treated as a new submission, and the referees were instructed not to give a full review. Moreover, their reviews have in our view been unfairly coloured by the previous reviews from the SISC submission which were provided to them. In particular, they criticise us due to \emph{"the computed example provides no information about whether or not the proposed method will work in the (sizable) applications mentioned in your introduction."} However, all mentions of such sizable applications have been completely removed from the introduction. The referees were responding to the reviews of the original paper which were sent to them, rather than the new paper, where these issues are not present.

@@

We are keen to resubmit the manuscript to SIAM/ASA JUQ for a second time. In order to address the issues that have arisen, we have provided three copies of the paper. The first is a latexdiff pdf of the changes that were made for our submission to SIAM/ASA JUQ from the original submission to SISC. The second is a latexdiff pdf of the changes we have made in our latest submission. The third version is our new submission. We also provide detailed descriptions of how the changes address the concerns of the referees.

@@

We thank you very much for your time and patience in dealing with this manuscript. We look forward to hearing from you in due course.
